---
title: "Figures_paper"
author: "Andres Baeza"
date: "July 5, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Read USA map
```{r}

#require(USAboundaries)
require(raster)
USA_map_full<-maptools::readShapeSpatial("C:/Users/abaezaca/Dropbox (ASU)/Design Principles in CIS/maps_USA/tl_2017_us_state/tl_2017_us_state")
top = 49.3457868 # north lat
left = -124.7844079 # west long
right = -66.9513812 # east long
bottom =  24.7433195 # south lat
USA_map<-raster::crop(USA_map_full,raster::extent(left,right,bottom,top))
USA_map@data$NAME<-factor(USA_map@data$NAME)
```


Figure 2: past present and future climate 
```{r,cache=TRUE}
require(raster)
#load climate variables


load("mean_annual_temperature_1950-2000_predictor1_object")
Tmean_m=Tmean_m/10

load("Total_annual_rainfall_1950-2000_predictor2_object") #PPT_m

load("mean_annual_temperature_1900-1950_predictor1_object")
Tmean_historic_m=Tmean_historic_m/10
load("annual_total_rainfall_raster_historico")#PPT_m_H
total_annual_rainfall_h=PPT_m_H

#load climate scenarios from "future_scenarios.Rmd"
load("Climate_Scenario_4")
TT_annual_S4<-scanario_4[[1]]
RR_annual_S4<-scanario_4[[2]]
#create R2
multiple_rainfall=PPT_m^2
#stack predictors
predictors<-stack(Tmean_m,
                  PPT_m,multiple_rainfall)
############################################################################
#figure 1
png(filename = "PastPresentandFutureClimate.png",width = 22,height = 12,units = "cm",res = 300)

par(mfrow=c(2,3))
#Temperature
image(Tmean_historic_m,zlim=c(-10,30),  col = rev(RColorBrewer::brewer.pal(9, "RdYlBu")),  xlab = 'Longitude', ylab = 'Latitude', main = 'A)  Ave. daily Temp. [1900-1950]',breaks=c(-11,-5,0,5,10,15,20,25,30,100))
plot(USA_map,add=T)

image(Tmean_m,zlim=c(-11,30),  col = rev(RColorBrewer::brewer.pal(9, "RdYlBu")),  xlab = 'Longitude', ylab = 'Latitude', main = 'B) [1951-2000]',breaks=c(-11,-5,0,5,10,15,20,25,30,100))
plot(USA_map,add=T)

TT_annual_S4_R=rotate(TT_annual_S4)
image(mask(TT_annual_S4_R,USA_map),zlim=c(-11,30),  col = rev(RColorBrewer::brewer.pal(9, "RdYlBu")),  xlab = 'Longitude', ylab = 'Latitude', main = 'C)   [2080-2010]',breaks=c(-11,-5,0,5,10,15,20,25,30,100))
plot(USA_map,add=T)


#precipitation
image(PPT_m_H,zlim=c(0,16),  col = RColorBrewer::brewer.pal(9, "YlGn"),  xlab = 'Longitude', ylab = 'Latitude', main = 'D)  Ave. daily Rainfall [1900-1950]',breaks=c(0,2,4,6,8,10,12,14,16,100))
plot(USA_map,add=T)

image(PPT_m,zlim=c(0,16),  col = RColorBrewer::brewer.pal(9, "YlGn"),  xlab = 'Longitude', ylab = 'Latitude', main = 'E)  [1950-2000]',breaks=c(0,2,4,6,8,10,12,14,16,100))
plot(USA_map,add=T)

RR_annual_S4_R=rotate(RR_annual_S4)
image(mask(RR_annual_S4_R,USA_map),zlim=c(0,16),  col = RColorBrewer::brewer.pal(9, "YlGn"),  xlab = 'Longitude', ylab = 'Latitude', main = 'F) 2080-2100',breaks=c(0,2,4,6,8,10,12,14,16,100))
plot(USA_map,add=T)

dev.off()


#scale
png(filename = "Scale_Climate.png",width = 10,height = 10,units = "cm",res = 300)
colfunc_R<-RColorBrewer::brewer.pal(9, "YlGn")
colfunc_T<-rev(RColorBrewer::brewer.pal(9, "RdYlBu"))
plot(rep(1,9),col=colfunc_R, pch=15,cex=4,bty="n",axes=F,ylab="",xlab="")
points(rep(1.2,9),col=colfunc_T, pch=15,cex=4)
text(x=1:9,y=rep(0.85,9),labels=c(0,2,4,6,8,10,12,14,"16<"),cex=0.8)
text(x=1:9,y=rep(1.3,9),labels=c(-11,-5,0,5,10,15,20,25,"30<"),cex=0.8)
dev.off()
```


Figure 1: past and current precence of _P. glandulosa_

```{r}
load("Prosopis_glandulosa_presence_data")#presence data
load("c:/Users/abaezaca/Dropbox (ASU)/Mesquite/Mesquite-distribution/Mesquite_distribution/PresencesNotUsed_obj")#presences_NotUsed

llmespg_H<-cbind(mesquite_pg_clean$lon[which(mesquite_pg_clean$year<1950)], mesquite_pg_clean$lat[which(mesquite_pg_clean$year<1950)])
presvals_pg_H<-as.data.frame(extract(predictors, llmespg_H))

presences_NotUsed_H=llmespg_H[-which(presvals_pg_H$var1.pred.1>0),]
llmespg_H=llmespg_H[which(presvals_pg_H$var1.pred.1>0),]

llmespg_C<-cbind(mesquite_pg_clean$lon[which(mesquite_pg_clean$year>1950)], mesquite_pg_clean$lat[which(mesquite_pg_clean$year>1950)])

presvals_pg_C<-as.data.frame(extract(predictors, llmespg_C))
llmespg_C=llmespg_C[which(presvals_pg_C$var1.pred.1>0),]



#llmespg_C<-llmespg_C[,-which(llmespg_C[,2]<0)]
#llmespg_H<-llmespg_H[,-which(llmespg_H[,2]<0)]

png(filename = "Presence_data_FigurePaper.png",width = 18,height = 10,units = "cm",res = 300)

par(mfrow=c(1,2),mar=c(1,2,1,2))

maps::map("usa",fill = T,col="grey")
box(which = "plot")
points(llmespg_H[,1],llmespg_H[,2],col=RColorBrewer::brewer.pal(9, "BrBG")[9],pch=20,cex=0.1)

legend(x=-120,y=48,legend = "Before 1950",col = "grey",bty = "n",pch =20,cex=0.6)


maps::map("usa",fill = T,col="grey")
box(which = "plot")
points(llmespg_C[,1],llmespg_C[,2],col=RColorBrewer::brewer.pal(9, "BrBG")[9],pch=20,cex=0.1)


legend(x=-120,y=48,legend = "After 1950",col = "grey",bty = "n",pch =20,cex=0.6)

dev.off()

#############plot presences outside usa####################
maps::map("usa",fill = T,col="grey")
box(which = "plot")
points(presences_NotUsed[,1],presences_NotUsed[,2],col=RColorBrewer::brewer.pal(9, "YlOrRd")[9],pch=20,cex=0.2)
points(presences_NotUsed_H[,1],presences_NotUsed_H[,2],col=RColorBrewer::brewer.pal(9, "YlOrRd")[9],pch=20,cex=0.2)

############
Avance_mesquite<-as.data.frame(cbind(mesquite_pg_clean$lon, mesquite_pg_clean$lat))


Avance_mesquite_USA<-as.data.frame(extract(predictors,Avance_mesquite))
Avance_mesquite_USA=Avance_mesquite_USA[which(Avance_mesquite_USA$var1.pred.1>0),]

```


Figure 3
```{r,cache=TRUE}
load("/data/prosopis_glandulosa_GLM_H_outputs")#glm_hist_outputs T50
load("prosopis_glandulosa_BIOCLIM_H_outputs")#bioclim_hist_outputs
load("prosopis_glandulosa_GAM_H_outputs") #gam_hist_outputs


load("prosopis_glandulosa_GLM_C_outputs") # glm_current_outputs
load("prosopis_glandulosa_BIOCLIM_C_outputs") # bioclim_curr_outputs
load("prosopis_glandulosa_GAM_C_outputs") #gam_curr_outputs


#future
load("GLM_scenario_85")#GLM_F  P2100
load("BIOCLIM_scenario_85")#BIOCLIM_F P2100
load("GAM_F_scenario_85")#GAM_F  P2100


png(filename = "Figure3.png",width = 30,height = 10,units = "cm",res = 300)
par(mfrow=c(1,3))
image(glm_hist_outputs[[4]]>glm_hist_outputs[[3]]@t[which.max(glm_hist_outputs[[3]]@TPR+glm_hist_outputs[[3]]@TNR)],col=c("grey",RColorBrewer::brewer.pal(9, "YlOrRd")[9]),ylab="Lat.",xlab="Long.",main="Past")
plot(USA_map,add=T)

image(glm_current_outputs[[4]]>glm_current_outputs[[3]]@t[which.max(glm_current_outputs[[3]]@TPR+glm_current_outputs[[3]]@TNR)],col=c("grey",RColorBrewer::brewer.pal(9, "YlOrRd")[9]),ylab="Lat.",xlab="Long.",main="Present")
plot(USA_map,add=T)

GLM_F_tmp=GLM_F[[2]]
GLM_C=glm_current_outputs[[4]]
GLM_F_tmp<-rotate(GLM_F_tmp)
crs(GLM_C)<-crs(GLM_F_tmp)
GLM_Fcr<-crop(GLM_F_tmp,GLM_C)


image(GLM_Fcr>glm_current_outputs[[3]]@t[which.max(glm_current_outputs[[3]]@TPR+glm_current_outputs[[3]]@TNR)],col=c("grey",RColorBrewer::brewer.pal(9, "YlOrRd")[9]),ylab="Lat.",xlab="Long.",main="Future")
plot(USA_map,add=T)

dev.off()

png(filename = "PastPresentFuture.png",width = 22,height = 20,units = "cm",res = 300)
par(mfrow=c(3,3))


#row 1)
image(glm_hist_outputs[[4]]>glm_hist_outputs[[3]]@t[which.max(glm_hist_outputs[[3]]@TPR+glm_hist_outputs[[3]]@TNR)],col=c("grey",RColorBrewer::brewer.pal(9, "YlOrRd")[9]),ylab="Lat.",xlab="Long.",main="Past")
plot(USA_map,add=T)

image(glm_current_outputs[[4]]>glm_current_outputs[[3]]@t[which.max(glm_current_outputs[[3]]@TPR+glm_current_outputs[[3]]@TNR)],col=c("grey",RColorBrewer::brewer.pal(9, "YlOrRd")[9]),ylab="Lat.",xlab="Long.",main="Present")
plot(USA_map,add=T)

#image(GLM_F[[2]]>glm_current_outputs[[3]]@t[which.max(glm_current_outputs[[3]]@TPR+glm_current_outputs[[3]]@TNR)],col=c("grey",RColorBrewer::brewer.pal(9, "YlOrRd")[9]),ylab="Lat.",xlab="Long.",main="Future")
#plot(USA_map,add=T)


GLM_F_tmp=GLM_F[[2]] #P2010
GLM_C=glm_current_outputs[[4]]
GLM_F_tmp<-rotate(GLM_F_tmp)
crs(GLM_C)<-crs(GLM_F_tmp)
GLM_Fcr<-crop(GLM_F_tmp,GLM_C)


image(GLM_Fcr>glm_current_outputs[[3]]@t[which.max(glm_current_outputs[[3]]@TPR+glm_current_outputs[[3]]@TNR)],col=c("grey",RColorBrewer::brewer.pal(9, "YlOrRd")[9]),ylab="Lat.",xlab="Long.",main="Future")
plot(USA_map,add=T)


#row 2) GAM
image(gam_hist_outputs[[4]]>gam_hist_outputs[[3]]@t[which.max(gam_hist_outputs[[3]]@TPR+gam_hist_outputs[[3]]@TNR)],col=c("grey",RColorBrewer::brewer.pal(9, "YlOrRd")[9]),ylab="Lat.",xlab="long.")
plot(USA_map,add=T)

image(gam_curr_outputs[[4]]>gam_curr_outputs[[3]]@t[which.max(gam_curr_outputs[[3]]@TPR+gam_curr_outputs[[3]]@TNR)],col=c("grey",RColorBrewer::brewer.pal(9, "YlOrRd")[9]),ylab="Lat.",xlab="long.")
plot(USA_map,add=T)

#image(GAM_F[[2]]>gam_curr_outputs[[3]]@t[which.max(glm_current_outputs[[3]]@TPR+glm_current_outputs[[3]]@TNR)],col=c("grey",RColorBrewer::brewer.pal(9, "YlOrRd")[9]),ylab="Lat.",xlab="long.")
#plot(USA_map,add=T)

GAM_F_tmp=GAM_F[[2]]

GAM_C=gam_curr_outputs[[4]]
GAM_F_tmp<-rotate(GAM_F_tmp)
crs(GAM_C)<-crs(GAM_F_tmp)
GAM_Fcr<-crop(GAM_F_tmp,GAM_C)


image(GAM_Fcr>gam_curr_outputs[[3]]@t[which.max(gam_curr_outputs[[3]]@TPR+gam_curr_outputs[[3]]@TNR)],col=c("grey",RColorBrewer::brewer.pal(9, "YlOrRd")[9]),ylab="Lat.",xlab="long.")
plot(USA_map,add=T)



#row 3)
image(bioclim_hist_outputs[[2]]>bioclim_hist_outputs[[3]]@t[which.max(bioclim_hist_outputs[[3]]@TPR+bioclim_hist_outputs[[3]]@TNR)],col=c("grey",RColorBrewer::brewer.pal(9, "YlOrRd")[9]),ylab="Lat.",xlab="long.")
plot(USA_map,add=T)

image(bioclim_curr_outputs[[2]]>bioclim_curr_outputs[[3]]@t[which.max(bioclim_curr_outputs[[3]]@TPR+bioclim_curr_outputs[[3]]@TNR)],col=c("grey",RColorBrewer::brewer.pal(9, "YlOrRd")[9]),ylab="Lat.",xlab="long.")
plot(USA_map,add=T)

#image(BIOCLIM_F[[1]]>bioclim_curr_outputs[[3]]@t[which.max(bioclim_curr_outputs[[3]]@TPR+bioclim_curr_outputs[[3]]@TNR)],col=c("grey",RColorBrewer::brewer.pal(9, "YlOrRd")[9]),ylab="Lat.",xlab="long.")
bioclim_F_tmp=BIOCLIM_F[[1]]

bioclim_C=bioclim_curr_outputs[[2]]
bioclim_F_tmp<-rotate(bioclim_F_tmp)
crs(bioclim_C)<-crs(bioclim_F_tmp)
bioclim_Fcr<-crop(bioclim_F_tmp,bioclim_C)


image(bioclim_Fcr>bioclim_curr_outputs[[3]]@t[which.max(bioclim_curr_outputs[[3]]@TPR+bioclim_curr_outputs[[3]]@TNR)],col=c("grey",RColorBrewer::brewer.pal(9, "YlOrRd")[9]),ylab="Lat.",xlab="long.")
plot(USA_map,add=T)

dev.off()

rm(gam_hist_outputs)
rm(gam_curr_outputs)
rm(bioclim_hist_outputs)
rm(bioclim_curr_outputs)
rm(GAM_C)
rm(GAM_F_tmp)
rm(bioclim_C)
rm(bioclim_F_tmp)

```


Figure 4
Panel 1 Diff modelo_H clima_H (T50) vs modelo C clima C T2000 - T50 
Panel 2 diff Modelo_C clima_C vs. modelo C Clima F T2000 - P2100
Panel 3 Diff Modelo_H clima F vs 

```{r}
Diff_HC<-(glm_hist_outputs[[4]]>glm_hist_outputs[[3]]@t[which.max(glm_hist_outputs[[3]]@TPR+glm_hist_outputs[[3]]@TNR)])-(glm_current_outputs[[4]]>glm_current_outputs[[3]]@t[which.max(glm_current_outputs[[3]]@TPR+glm_current_outputs[[3]]@TNR)])


GLM_C=glm_current_outputs[[4]]
GLM_F_tmp=GLM_F[[2]]

GLM_F_tmp<-rotate(GLM_F_tmp)
crs(GLM_C)<-crs(GLM_F_tmp)
GLM_Fcr<-crop(GLM_F_tmp,GLM_C)

GLM_C_v2=projectRaster(from = GLM_C,to = GLM_Fcr)

B1=(GLM_C_v2>glm_current_outputs[[3]]@t[which.max(glm_current_outputs[[3]]@TPR+glm_current_outputs[[3]]@TNR)])
B2=GLM_Fcr>glm_current_outputs[[3]]@t[which.max(glm_current_outputs[[3]]@TPR+glm_current_outputs[[3]]@TNR)]

Diff_CF=(B1-B2)


###########################figure
png(filename = "Expansion.png",width = 22,height = 10,units = "cm",res = 300)

par(mfrow=c(1,2))
image(Diff_HC,col=c("magenta4","grey","grey"),ylab="Lat.",xlab="Long.",main="Expansion from pass to present")
plot(USA_map,add=T)
#legend("topright",legend = c("Expansion from pass to present","no differences"),pch = 15,fill = T,col = c("magenta4","grey"))


image(as.factor(Diff_CF)==-1,col=c("grey","yellow"),ylab="Lat.",xlab="Long.",main="Expansion from present to future")
plot(USA_map,add=T)

dev.off()


```
Differences in past and present GLM predictions


Figure 5
```{r,cache=TRUE}

load("prosopis_glandulosa_GLM_H_outputs")#glm_hist_outputs T50
T50=glm_hist_outputs[[4]]>glm_hist_outputs[[3]]@t[which.max(glm_hist_outputs[[3]]@TPR+glm_hist_outputs[[3]]@TNR)]
rm(glm_hist_outputs)

crs(T50) <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0" 


load("Turing_scenarios2000")#Turing_Scenarios T2000
T2000=Turing_Scenarios[[1]]
rm(Turing_Scenarios)
crs(T2000) <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0" 


load("Turing_scenariosFutureClimate")#Turing_Scenarios future climate T2100
T2100=Turing_Scenarios_FC[[1]]
rm(Turing_Scenarios_FC)


crs(T2100) <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0" 



T2100 %>%
  disaggregate(fact=res(T2100)/res(T50))%>%
#T2100_Disagre=resample(T50,T2100)
rotate()%>%
#crs(P2000)<-crs(T2100)

projectRaster(to = T50)%>%

crop(T50)-> T2100_F

#####################P2100####################

load("prosopis_glandulosa_GLM_C_outputs") # glm_current_outputs P2000
P2000=glm_current_outputs[[4]]>glm_current_outputs[[3]]@t[which.max(glm_current_outputs[[3]]@TPR+glm_current_outputs[[3]]@TNR)]
crs(P2000) <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0" 

P2000%>%
disaggregate(fact=res(P2000)/res(T50))%>%

#P2000=rotate(P2000_Disagre)
crop(T50>(-0.1))->P2000_F

#P2000=projectRaster(from = P2000,to = T50)



load("GLM_scenario_85")  #P2100
P2100=GLM_F[[2]]>glm_current_outputs[[3]]@t[which.max(glm_current_outputs[[3]]@TPR+glm_current_outputs[[3]]@TNR)]
rm(GLM_F)
rm(glm_current_outputs)
crs(P2100) <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0" 

P2100%>%
disaggregate(fact=res(P2100)/res(T50))%>%

rotate()%>%

projectRaster(to = T50)%>%

crop(T50>(-0.1))-> P2100_F


######################################################
#Figure##########################################
###################################################

png(filename = "Figure3_V2.png",width = 60,height = 30,units = "cm",res = 200)
par(mfrow=c(2,3),cex=1.2)

image(T50,col=c("grey",RColorBrewer::brewer.pal(9, "YlOrRd")[9]),ylab="Lat.",xlab="Long.",main="A)     T50")
plot(USA_map,add=T)

image(T2000,col=c("grey",RColorBrewer::brewer.pal(9, "YlOrRd")[9]),ylab="Lat.",xlab="Long.",main="B)     T2000")
plot(USA_map,add=T)

image(mask(T2100_F,USA_map),col=c("grey",RColorBrewer::brewer.pal(9, "YlOrRd")[9]),ylab="Lat.",xlab="Long.",main="C)     T2100")
plot(USA_map,add=T)

image(P2000_F,col=c("grey",RColorBrewer::brewer.pal(9, "YlOrRd")[9]),ylab="Lat.",xlab="Long.",main="D)     P2000")
plot(USA_map,add=T)

image(P2000_F,col=c("grey",RColorBrewer::brewer.pal(9, "YlOrRd")[9]),ylab="Lat.",xlab="Long.",main="D)     P2000")
plot(USA_map,add=T)

image(mask(P2100_F,USA_map),col=c("grey",RColorBrewer::brewer.pal(9, "YlOrRd")[9]),ylab="Lat.",xlab="Long.",main="E)     P2100")
plot(USA_map,add=T)

dev.off()
##Raster operations

Diff_T50T2000=T2000-T50 #current expansion due to climate

Diff_P2000T2000=(P2000_F - T2000)  # P2000- T2000 current expasion due to Land-use change

DiffP2000_T50= P2000_F - T50   #total current expansion


#Diff_T50T2100=(T2100>0)-T50 #future expansion due to climate
Diff_T2100P2000=(T2100_F>0)-P2000_F #future expansion due to climate


DiffP2100_T2100=mask((P2100_F-(T2100_F>0)),USA_map) #future expansion due to LU #Note: use mask() function ro remove areas outside USA

#DiffP2100_T50=P2100 - T50 #Total expansion due to climate and LU

DiffP2100_P2000=P2100_F - P2000_F #Total expansion due to climate and LU



png(filename = "Drivers_of_expansion_D.png",width = 60,height = 30,units = "cm",res = 200)
par(mfrow=c(2,3),cex=1.2)

image(Diff_T50T2000>0.5,col=c("grey","darkgreen"),ylab="Lat.",xlab="Long.",main="A)   Current [C]")
plot(USA_map,add=T)

image(Diff_P2000T2000>0,col=c("grey","yellow"),ylab="Lat.",xlab="Long.",main="B)    Current [LU]")
plot(USA_map,add=T)

image(DiffP2000_T50>0,col=c("grey","red"),ylab="Lat.",xlab="Long.",main="C)   Current [C + LU]")
plot(USA_map,add=T)

image(Diff_T2100P2000>0.5,col=c("grey","darkgreen"),ylab="Lat.",xlab="Long.",main="D)   Future [C]")
plot(USA_map,add=T)

image(DiffP2100_T2100,col=c("grey","yellow"),ylab="Lat.",xlab="Long.",main="E)   Future [LU]")
plot(USA_map,add=T)

image(DiffP2100_P2000>0.5,col=c("grey","red"),ylab="Lat.",xlab="Long.",main="F)   Future [C + LU]")
plot(USA_map,add=T)
dev.off()


```


####extract area by state and create a csv value file
```{r,cache=TRUE}
A=area(Diff_T50T2000)
Current_expansion_climate_area= extract((A*(Diff_T50T2000>0)),USA_map,fun=sum)

Current_expansion_LU_area= extract((A*(Diff_P2000T2000>0)),USA_map,fun=sum)

Current_expansion_LU_C_area= extract((A*(DiffP2000_T50>0)),USA_map,fun=sum)

Future_expansion_climate_area= extract((A*(Diff_T2100P2000>0)),USA_map,fun=sum)

Future_expansion_LU_area= extract((A*(DiffP2100_T2100>0)),USA_map,fun=sum)

Future_expansion_LU_C_area= extract((A*(DiffP2100_P2000>0)),USA_map,fun=sum)


area_perState=cbind(Current_expansion_climate_area,
Current_expansion_LU_area,
Current_expansion_LU_C_area,
Future_expansion_climate_area,
Future_expansion_LU_area,
Future_expansion_LU_C_area)

area_perState<-as.data.frame((area_perState))
rownames(area_perState)<-USA_map$NAME
colnames(area_perState)=c("C_C","C_LU","C_C_LU","F_C","F_LU","F_C_LU")
View(area_perState)
write.csv(area_perState,file = "table_expansion_AreabyState.csv")
#area_perState=read.csv("table_expansion_AreabyState.csv")
#area_perState$X<-USA_map$NAME
```


#Table parameters
```{r,cache=TRUE}
load("prosopis_glandulosa_GLM_H_outputs")
load("prosopis_glandulosa_GLM_C_outputs") 

load("prosopis_glandulosa_GAM_H_outputs")
load("prosopis_glandulosa_GAM_C_outputs") 

#load("prosopis_glandulosa_BIOCLIM_H_outputs")#glm_hist_outputs T50
#load("prosopis_glandulosa_BIOCLIM_C_outputs") # glm_current_outputs P2000



coef_glm_Hist_Current=rbind(coef(glm_hist_outputs[[1]]),
coef(glm_current_outputs[[1]]))

rownames(coef_glm_Hist_Current)<-c("T-model","P-model")

write.csv(coef_glm_Hist_Current,file="coef_glm_Hist_Current.csv")
res_comparsion_parameters=(coef(glm_hist_outputs[[1]])-coef(glm_current_outputs[[1]]))#/(coef(glm_hist_outputs[[1]])+coef(glm_current_outputs[[1]]))
```


# Calculate total area (in km2) for the predicted distributions T50, T2000, T2100, P2000, and P2100.

```{R}
A=area(T50)

T50_area= cellStats(A*(T50>0),stat ="sum")

T2000_area= cellStats(A*(T2000>0),stat ="sum")

T2100_area= cellStats(A*(T2100_F>0),stat ="sum")

P2000_area= cellStats(A*(P2000_F>0),stat ="sum")

P2100_area= cellStats(A*(P2100_F>0),stat ="sum")

area_table=data.frame(matrix(data = c(T50_area,T2000_area,T2100_area,NA,P2000_area,P2100_area),nrow = 2,ncol = 3,byrow = T))
View(area_table)
colnames(area_table)<-c("Past Climate","Current Climate","Future Climate")
rownames(area_table)<-c("Model T","Model P")
write.csv(x = area_table,file = "area_table_in_kmsquared.csv")
```
